---
title: "lab7.rmd"
author: "Shawn Vizgan"
date: "10/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
question 1)
```{r}
?binom.test
binom.test(x = 30,
           n = 50,
           p = .5,
           alternative='greater')


#the pvalue is .1, and is higher than p < .05, meaning that it is 10% possible to get this score by chance and with random guessing and is not considered to be especially significant.



#100/100
```


question 2)
```{r}

binom.test(385,700,.5,alternative="greater")






#100/100 but confirmed my thought using the video
```

question 3)
```{r}
# task_designs <- data.frame( number_of_heads = 0:5, true_or_false = 0:5, 
#                           probability1 = dbinom(x=0:1,size=1,prob= .5),
#                           cumulative1 = pbinom(0:1, size = 1, prob = .5),
#                           rev_cumulative1 = pbinom(-1:0, 1, .5, lower.tail=FALSE),
#                           probability2 = dbinom(x=0:1,size=1,prob= .25),
#                           cumulative2 = pbinom(0:1, size = 1, prob = .25),
#                           rev_cumulative2 = pbinom(-1:0, 1, .25, lower.tail=FALSE))
# knitr::kable(task_designs)

rbinom (n= rep(1,10), size = 1, prob = c(.5,.5,.5,.5,.5,.25,.25,.25,.25,.25) )

simulated_test <- replicate(10000, rbinom (n= rep(1,10), size = 1, prob = c(.5,.5,.5,.5,.5,.25,.25,.25,.25,.25) ))

simulated_scores <- colSums(simulated_test)/10

library(ggplot2)

qplot(simulated_scores)+
  geom_histogram()
  

length(simulated_scores[simulated_scores > .75]) /10000



#0/100 i was confused as hell and my own attempt was not effective
