---
title: "lab8.rmd"
author: "Shawn Vizgan"
date: "11/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


## Including Plots




Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
1)Write a function to convert a vector of raw-scores into z-scores. The function should have inputs for the vector, the mean and sd of the normal distribution, and should return a vector of zscores. (1 point). Also, demonstrate that the function works correctly (1 point). How you make the demonstration is up to you.
Advanced: Have an option so that the function will convert the raw scores to zscores in one of two ways:
using user provided mean and standard deviation
using the calculated mean and standard deviation from the raw scores
```{r}
sample_means <- rnorm(1000,25,5)

specialsample <- sample((sample_means), 10 , replace = FALSE)


z_test <- function(raw, mu, standard_dev){
  zscores <- (raw-mu)/standard_dev
  return(zscores)
}

z_test(raw = specialsample, mu = mean(sample_means), standard_dev = sd(sample_means))

##z_score <- function(x){
  ##(x-mean(x))/sd(x)
##}

##z_score(c(1,2,3,4,5,6,7,7))

```

Base R does not have a function for a z-test. Write a function to accomplish a one-sample z-test. Remember, a one-sample z test is used to compare the probability of obtaining the sample mean (or larger or smaller) if it came from a known normal distribution. (2 points).
Use your z-test function to conduct a test of the following. A sample of 25 scores is taken. The mean of the sample is 50. The sample is assumed to have been taken from a normal distribution with mean 40 and standard deviation 7. Report a one-tailed z-test, examining the probability of obtaining a sample of greater than 50 in this situation. Report the results, and give a brief sentence explaining the result and the inference you make (2 points).
```{r}

z.test <- function(sample_mean,sample_size,mu,sigma){
  smpl_dist_mean <- mu
  smpl_dist_sd <- sigma/sqrt(sample_size)
  
  p_value <- pnorm(sample_mean,smpl_dist_mean,smpl_dist_sd, lower.tail = FALSE)
  return(p_value)
  
}

z.test(sample_mean = 50,
       sample_size = 25, 
       mu = 40,
       sigma = 7)

## p < .05, it is a significant result to get a value of 50 from a distribution with a population mean of 40, there would be a higher likelihood that 50 might more likely come from an alternative distribution than come from this distribution by chance.


```